False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2016-05-10 document/ms.tex
added github comment to paper; submitted to arxiv

\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}

@@

%\author{Timothy D. Morton}
%\affil{Department of Astrophysical Sciences, Princeton University}
\author{Timothy D. Morton\altaffilmark{1}, Stephen T. Bryson\altaffilmark{2}, Jeffrey L. Coughlin\altaffilmark{2,3}, Jason F. Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A. Petigura\altaffilmark{6}, 
Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA, tdm@astro.princeton.edu}
\altaffiltext{2}{NASA Ames Research Center, M/S 244-30, Moffett Field, CA 94035, USA}
\altaffiltext{3}{SETI Institute, 189 Bernardo Ave, Mountain View, CA 94043, USA}
\altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
\altaffiltext{5}{Columbia University}
\altaffiltext{6}{California Institute of Technology}

@@

>>>>

%\slugcomment{note: this work is UNDER EMBARGO until publicly announced.}

@@

%\author{Timothy D. Morton}
%\affil{Department of Astrophysical Sciences, Princeton University}
\author{Timothy D. Morton\altaffilmark{1}, Stephen T. Bryson\altaffilmark{2}, Jeffrey L. Coughlin\altaffilmark{2,3}, Jason F. Rowe\altaffilmark{4}, Ganesh Ravichandran\altaffilmark{5}, Erik A. Petigura\altaffilmark{6,7}, 
Michael R. Haas\altaffilmark{2}, and Natalie M. Batalha\altaffilmark{2}}

@@

\altaffiltext{1}{Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA, tdm@astro.princeton.edu}
\altaffiltext{2}{NASA Ames Research Center, M/S 244-30, Moffett Field, CA 94035, USA}
\altaffiltext{3}{SETI Institute, 189 Bernardo Ave, Mountain View, CA 94043, USA}
\altaffiltext{4}{D\'epartement de Physique, Universit\'e de Montr\'eal, Montr\'eal, QC, Canada, H3T 1J4}
\altaffiltext{5}{Department of Computer Science, Columbia University, 1214 Amsterdam Ave, New York, NY 10027}
\altaffiltext{6}{California Institute of Technology, Pasadena, CA 91125, USA}
\altaffiltext{7}{Hubble Fellow}

@@

\vspace{1.5\baselineskip}
Instructions for reproducing all the calculations presented 
herein can be found at \url{https://github.com/timothydmorton/koi-fpp}.
Summary figures produced by \vespa\ for all KOIs can be accessed
at \url{http://kepler-fpp.space}.
